pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-19 manuscript/greenwell.tex
minor edits

Currently supported models are described in Table~\ref{tab:models}. In a lot of these cases, \code{partial} should be able to automatically determine \code{type} (i.e., \code{"regression"} or \code{"classification"}) and \code{train} (the original training data). In other cases, the user may need to specify these additional arguments. Using these additional arguments, it is possible to handle many of the model types not listed in in this table; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.

>>>>

Currently supported models are described in Table~\ref{tab:models}. In a lot of these cases, \code{partial} should be able to automatically determine \code{type} (i.e., \code{"regression"} or \code{"classification"}) and \code{train} (the original training data). In other situations, the user may need to specify these additional arguments. This allows \code{partial} to be flexible enough to handle many of the model types not listed in in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.
